### 2016-03-10 paper1.tex
Made all references unique to this paper/chapter.

\subsection{Binary Formation in High-Mass Stars}
\label{sec:formation}
With such a high fraction of high-mass stars found in binary or multiple
systems, any theory of high-mass star formation should be able to
explain the high binary formation rate. There are several mechanisms by
which binary stars may form: fission \citep{Lyttleton1953,
  Lebovitz1974, Lebovitz1984}, in which a molecular core begins
spinning fast enough as it collapses that it splits into two stars;
core fragmentation \citep[see e.g.][]{Boss1979, Boss1986, Bate1995}, in which a collapsing core develops two or more
overdensities which then begin collapsing separately; and disk
fragmentation \citep[see e.g.][]{Kratter2006, Stamatellos2011}, in which the circumstellar disk surrounding the primary
star becomes gravitationally unstable and creates a secondary
star. While the fission scenario was once thought to be important, it
has since fallen out of favor because the viscous dissipation timescale, which would drive a spinning body towards fission, is much longer than the core collapse timescale \citep{Tohline2002} and because hydrodynamic simulations fail to cause
the rotating core to actually split rather than just deform
\citep{Tohline2001}. Both core and disk fragmentation are still
thought to be viable binary formation mechanisms. It is likely that
both mechanisms play a role in shaping the binary mass-ratio and
separation distributions. In the formation of higher-order multiples, it is even possible that both mechanisms operate in the same system.

@@

\subsection{Observing low mass-ratio binaries}
\label{sec:otherobs}
Detection of OB-star binaries with mass-ratio $q \approx 0.1$ or lower is very
difficult, since the ratio of the secondary flux $F_s$ to the primary
flux $F_p$ is $F_s/F_p \sim 10^{-3}$ or lower in the V-band. Imaging surveys
can detect such contrast ratios for wide orbits, but lose sensitivity
as the separation decreases below about $1^{\prime\prime}$
\citep[e.g.][]{Maiz2010}. Spectroscopic binary surveys do well for
short-period systems where a full orbit can be mapped in a reasonable
amount of time, but lose sensitivity for periods greater than about one year
\citep[e.g.][]{Sana2009, Evans2010}. However, low-mass companions ($q \lesssim
0.2$), which induce a small reflex motion on the primary, are very difficult to find with
traditional spectroscopic surveys.

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig1.pdf}
  \caption{This figure illustrates the approximate flux ratio limit to
  the detection method outlined in section
  \ref{sec:newmethod}. \emph{Top panel}: Residuals after telluric
  correction (see section \ref{sec:reduction}) for chip 2 of HIP 80582 are in black, with an
  atmosphere model for an $0.9 M_{\odot}$ star at 50.1 Myr below it in
  red. The flux ratio at this age is $F_s/F_p = 0.0092$. \emph{Middle panel}: The scaled model
  spectrum was added to the telluric residuals, and then the sum was
  cross-correlated with the model. Despite the signal being
  significantly below the noise level, the star was detected at a high
significance. The y axis, in units of the standard deviation of the
cross-correlation function, shows that the significance of the peak is over
$4\sigma$. \emph{Bottom panel}: Same as the middle panel, but the
model spectrum was added to the residuals with a 50 km s$^{-1}$ velocity
offset.}
  \label{method}
\end{figure*}

In this paper, we introduce a technique that is sensitive to young binary
systems with secondary temperatures $4000$ K $\lesssim T_\mathrm{eff} \lesssim
6000 $K. For early B-type primaries with ages $\sim 15$ Myr, these
temperatures correspond to mass-ratios $q \approx 0.05-0.3$, right
where we expect to see binaries formed by disk instability (see
section \ref{sec:formation}). Rather
than attempting to detect the reflex motion of the parent
star as in exoplanet searches and SB1 binaries, we attempt to directly
detect the spectrum of the young low-mass companion using high
signal-to-noise, high-resolution data. There is a multitude of archived B-star observations in the near-infrared,
where they are used as telluric standard stars to remove the absorption spectrum of the Earth's atmosphere (telluric
lines). This method is equally sensitive to all separations within the point spread function, which is dominated by the seeing since the adaptive optics are not used in telluric standard star observations. A typical seeing of $\sim 0.8''$ corresponds to up to $\sim 900$ AU for targets within a few kpc. In this paper, we describe a search for young F5-K9 type companions in archived VLT/CRIRES spectra of 34 early B-type stars.

In section \ref{sec:newmethod} we describe our detection method in 
more detail. Section \ref{sec:sample} describes the B-star sample we use in this work.
Section \ref{sec:reduction} contains the data reduction and telluric correction methods. 
We summarize our results in section \ref{sec:results}. We examine the
completeness of our sample in section \ref{sec:completeness} and put
limits on the multiplicity fraction as a function of mass-ratio in
section \ref{sec:multiplicity}. Finally, we present our conclusions about the prevalence of low mass-ratio companions to early B-type stars and discuss how our results constrain star formation mechanisms in Section \ref{sec:conclusions}.

\section{Direct Spectral Detection Method}
\label{sec:newmethod}

We describe here our method to detect the emission from an
approximately solar-mass star orbiting an early B-type star, which we
will hereafter call the direct spectral detection method. The basis of
this method is to cross-correlate a high signal-to-noise ratio B-star
spectrum with a synthetic F,G, or K star spectrum. If a low-mass star
with such a spectrum is orbiting the B-star, we expect to find a peak
in the cross-correlation function at the radial velocity corresponding to
the low-mass star's motion. A peak in the cross-correlation
function should appear even if the
flux from the low-mass star is comparable to or even slightly less than the noise level in the
spectrum. Figure \ref{method} illustrates the approximately limiting
case for the flux ratio. The top panel shows a fully reduced CRIRES spectrum of HIP 108975 (see section \ref{sec:reduction}) with a model spectrum for an $0.9 M_{\odot}$ star at a realistic flux ratio below it. We used
evolutionary tracks published by \cite{Landin2008} to evolve the secondary star
to 50.1 Myr, the age of the system \citep{Tetzlaff2010}, in order to determine the flux
ratio between the primary and secondary. The secondary star model was then added to
the telluric-corrected B-star spectrum at two different velocities. It is clear that the model spectrum has an amplitude much smaller
than the noise.  Nonetheless, the bottom two panels show that a cross-correlation will
have a peak with high significance at the velocity of the secondary star.

\begin{figure*}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig2.pdf}
  \caption{\emph{Top panel}: The telluric spectrum (absorption due to Earth's
    atmosphere) in the wavelength range from $2290-2400$ nm. Most of the lines are
    from CH$_4$, with a few H$_2$O lines appearing in the right
    half. \emph{Bottom panel}: The model spectrum of a 5500 K star
    with $\log (g) = 4.0$ and solar metallicity. Note that the line density of telluric
    lines is comparable to or greater than that of the star model, and many of the
    telluric lines are stronger than the stellar lines.}
  \label{telluric}
\end{figure*}

@@

There are two main difficulties with the direct spectral detection method: 
telluric line removal and the low flux ratio between the primary and secondary
star. Figure \ref{telluric} shows the transmittance through the
Earth's atmosphere (the telluric spectrum) in the wavelength range we
are interested in. Most of the spectral lines are from methane, with a
few deep water lines towards the red end
of the range shown (See section \ref{sec:reduction} for details on the
telluric line removal). The low flux ratio makes the telluric
contamination especially troublesome, since the telluric lines are
stronger than the lines in the companion star spectrum. The flux ratio of $F_s/F_p
\sim10^{-2}$ effectively sets a lower limit on the signal-to-noise
ratio for which the direct spectral detection method is possible. 
Any flux coming from a low-mass star will be completely buried
in the Poisson noise for spectra with SNR $\ll100$. Removal of the 
telluric contamination will add more noise to the spectrum, so a spectrum
should have SNR of a few hundred \emph{before telluric line removal}
to have a good chance of detecting a companion.

\section{Star Sample}
\label{sec:sample}
B-type stars are commonly used in the near-IR as telluric
standard stars. Astronomers will observe their science targets, and
then move to a B-type star. Since B-type stars have few
spectral lines relative to cooler stars, most of the observed
spectral lines will be from the absorption of Earth's atmosphere
(telluric absorption). Therefore, these stars provide an empirical
estimate of the telluric spectrum; division of the science spectrum by
the normalized standard star spectrum will mostly remove the telluric
lines.

@@

To generate the sample, we started with all single, main sequence B0-B5 stars 
with CRIRES observations from 2300-2400 nm. We then excluded any shell stars, which have circumstellar disks \citep{Porter2003} that may create
false positives. Table \ref{tab:sample} shows the complete sample used in this
project. The spectral types and ages were obtained from a catalog of nearby
young stars \citep{Tetzlaff2010}. The one exception is HIP 97611, which was
not in \cite{Tetzlaff2010}. For this star, the age was taken from
\cite{Westin1985} and the spectral type from the Simbad database\footnote{\url{http://simbad.u-strasbg.fr/simbad/}}
. The distances to all stars were
determined from parallaxes given in the Simbad database. The maximum
separation column estimates the approximate maximum separation of the binary
orbit we are sensitive to, assuming a seeing of 0.8'' which is typical of
Paranal Observatory. The median of the maximum separations to which we are sensitive is 124
AU.  The final column gives the number of distinct observations of the
star. We count all nodding positions taken on a given night with the same 
detector wavelength setting as one observation.

@@

\section{Data Reduction and Telluric Correction}
\label{sec:reduction}
The data reduction was done using standard methods in
IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatories,
    which are operated by the Association of Universities for Research
    in Astronomy, Inc., under cooperative agreement with the National
    Science Foundation.}. All observations were taken in an AB or ABBA nodding
pattern. For each set of AB nods, A-B and B-A frames were made to
remove any atmospheric emission lines and dark current. The resulting
difference images were then treated to a quadratic nonlinearity correction, using
coefficients made available by the CRIRES
team%\footnote{\url{http://www.eso.org/observing/dfo/quality/CRIRES/pipeline/pipe_calib.html}}. 
The corrected frames were then divided by a normalized flat-field. Due
to the slit curvature, the spectrum can shift by up to a pixel in
the dispersion direction between the A and B nod positions. Therefore,
combining the 2D frames before extraction can reduce the spectral
resolution and affect the line shapes. For this reason, we
combined the nodding positions only after the wavelength
calibration and telluric correction. Each nod position was extracted using the 
optimal algorithm in the apall task in IRAF. The spectra were wavelength 
calibrated using a model telluric
spectrum generated with the atmospheric modeling code
LBLRTM%\footnote{\url{http://www.rtweb.aer.com/lblrtm_description.html}}
\citep{Clough2005}.

@@

The LBLRTM atmospheric modeling code comes with a molecular line list
based on the HITRAN 2008 database \citep{Rothman2009}, with a few
molecules individually updated. Since none of these updates were
relevant for the wavelength range from $2300 - 2400$ nm, we in
essence used the stock HITRAN 2008 database. However,
in the process of modeling, we found several water and methane lines
that were consistently under- or over-fit. For these cases, we
manually adjusted the line strengths in the database. The line
strengths were fit visually and should not be considered rigourous new line strengths. Table \ref{tab:linelist}
summarizes these changes.

@@

In order to minimize these spikes, we performed a second fit to any
residuals significantly above the continuum noise level. To make sure
we were not fitting away any low-mass star lines, we only corrected
spikes whose amplitude was greater than $5\%$ of the continuum level. In this
second fit, we first attempted to fit a Gaussian to each spike. If the
spike was well fit by a Gaussian, we divided the residuals by the fit.
If not, we
simply masked out the line core, so that it would not affect the
cross-correlation in later analysis (see section \ref{sec:newmethod}). Figure
\ref{correctionsteps} shows the steps involved in the telluric
correction. Notice that the secondary correction removes the
large residuals, while leaving the rest of the spectrum
unaffected.

@@

\section{Results}
\label{sec:results}
Each telluric residual spectrum was cross-correlated against a suite of model atmospheres
generated by the Phoenix stellar atmosphere code \citep{Hauschildt1999}. All model spectra had solar metallicity. The effective
temperatures ranged from $3000-7200$ K, in 100K intervals. We used
several surface gravities based on the stellar temperature. For the
model secondary stars with $3000 < T_\mathrm{eff} < 3600$, which would
have to be very young (and large) to be detectable, we used a $\log (g) = 3.5$. For the secondaries with
$3600 < T_\mathrm{eff} < 6500$, we used $\log (g) = 4.0$. Finally, we used
$\log (g) = 4.5$ for $T_\mathrm{eff} > 6500$, which can be detected
closer to the Main Sequence. We found that the surface gravity has only a very small
effect on the cross-correlation, which is more sensitive to the line
position than its precise width or depth. We
compiled a list of all cross-correlations that show a single peak with
at least $3\sigma$ significance. For a given telluric-corrected residual
spectrum, several model atmospheres may generate a significant peak at
the same velocity. This is because the model spectra of two stars
differing by only a few hundred kelvin are not very different. To keep from
counting peaks twice, we only counted the cross-correlation that
resulted in the most significant peak at a given velocity. We then attempted to
reject spurious peaks caused by the noise or incomplete telluric line
removal in a multi-stage process.

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig4.pdf}
  \caption{Cross-correlation for HIP 26713, using a 5600 K star model spectrum as template. The y-axis is in units of
    the standard deviation of the cross-correlation function. The peak is very near the maximum velocity of $|v_\mathrm{max}| = 256$ km s$^{-1}$, assuming a circular orbit (see equation \ref{eqn:vmax}). The likelihood of observing the system nearly edge on and at a quadrature point, so that $|v| \sim |v_\mathrm{max}|$, is $p \approx 0.01$. However, it is possible that the system has an eccentric orbit, effectively increasing $|v_\mathrm{max}|$.}
  \label{fig:hip26713}
\end{figure*}

Next, we determined whether the signal-to-noise ratio and telluric line removal in a given observation would allow us to detect the candidate companion star.
To do this, we added a model atmosphere with the
same temperature as the candidate to the telluric-corrected spectrum at 17 different radial
velocities ranging from -400 to 400 km s$^{-1}$. We do not expect to see any
peaks from real companions with $|v| > 400$ km s$^{-1}$, the approximate
radial velocity of a $1 M_{\odot}$ star orbiting a $10 M_{\odot}$ star
such that the stellar surfaces are in contact. The flux ratio of the model atmosphere to the primary was obtained by
interpolating pre-main-sequence evolutionary tracks from
\cite{Landin2008} at the age of the system, as well at age$\pm
\sigma_{age}$. The primary star ages for our sample are given in Table
\ref{tab:sample}. We cross-correlated each of these semi-synthetic
spectra against the model spectrum; if the largest
peak was at the correct velocity, we counted the star as
detected. If the star was not detected in the sensitivity
analysis at least $50\%$ of the time, we rejected the candidate.
The significance of the correct peak in the cross-correlation 
function can vary greatly, depending on where the stellar spectrum falls in 
relation to the telluric line residuals. Therefore, we cannot usually reject a peak
based solely on its significance.

@@

\begin{equation}
v_\mathrm{max} = \sqrt{\frac{2G(M_\mathrm{prim} + M_\mathrm{sec})}{R_\mathrm{prim}}} \cdot \frac{T_\mathrm{sec}}{T_\mathrm{prim}}
\label{eqn:vmax}
\end{equation}

where $M_\mathrm{prim}$ and $M_\mathrm{sec}$ are the masses of the primary and
secondary stars, respectively, and $R_\mathrm{prim}$ is the radius of the
primary star. The primary masses are given in \cite{Tetzlaff2010}, while
the radii and primary star temperatures were estimated from spectral type relations given in
\cite{CarrollOstlie}. An eccentric orbit could have a larger maximum velocity than
that estimated by equation \ref{eqn:vmax}, if the orbit was oriented
such that the the secondary star was moving directly towards or away from earth at or near
periastron. A star in an eccentric orbit cannot get so close to the
primary that they touch, and its \emph{average} distance must still be
far enough to allow for the observed secondary star temperature. These
conditions lead to a maximum eccentricity, given by

\begin{equation}
e_\mathrm{max} = 1 - \frac{v_\mathrm{max}^2 (R_\mathrm{prim} + R_\mathrm{sec})}{G(M_\mathrm{prim} + M_\mathrm{sec})}
\label{eqn:emax}
\end{equation}

where $R_\mathrm{prim} $ and $R_\mathrm{sec}$ are the radii of the primary
and secondary stars, respectively, and $v_\mathrm{max}$ is the maximum
circular velocity given by equation \ref{eqn:vmax}. Typical values
give $e_\mathrm{max} \approx 0.6$. Eccentricities near this value could
allow for velocities significantly greater than $v_\mathrm{max}$ given by
equation \ref{eqn:vmax}.

The above analysis is summarized in Table \ref{tab:rejection}. There
are two binary candidate systems that we have not been able to reject.
 For both of these, we checked what other observations the candidate
star had within the CO bandhead spectral region ($2300-2400$ nm). The analysis of each
of these stars is done separately below.

@@

\subsection{HIP 26713}
The cross-correlation for this candidate is shown in figure
\ref{fig:hip26713}. The strong peak at -220 km s$^{-1}$ has a
significance just over $4\sigma$, and corresponds to a 5600 K star
model. A sensitivity analysis (Table \ref{tab:rejection}, step 2) gives a median peak significance of $\sim 6\sigma$
with a large ($\sim 2\sigma$) spread. Due to the large spread, we cannot reject
the peak based on the observed significance.

>>>>

\subsection{Binary Formation in High-Mass Stars}
\label{paper1_sec:formation}
With such a high fraction of high-mass stars found in binary or multiple
systems, any theory of high-mass star formation should be able to
explain the high binary formation rate. There are several mechanisms by
which binary stars may form: fission \citep{Lyttleton1953,
  Lebovitz1974, Lebovitz1984}, in which a molecular core begins
spinning fast enough as it collapses that it splits into two stars;
core fragmentation \citep[see e.g.][]{Boss1979, Boss1986, Bate1995}, in which a collapsing core develops two or more
overdensities which then begin collapsing separately; and disk
fragmentation \citep[see e.g.][]{Kratter2006, Stamatellos2011}, in which the circumstellar disk surrounding the primary
star becomes gravitationally unstable and creates a secondary
star. While the fission scenario was once thought to be important, it
has since fallen out of favor because the viscous dissipation timescale, which would drive a spinning body towards fission, is much longer than the core collapse timescale \citep{Tohline2002} and because hydrodynamic simulations fail to cause
the rotating core to actually split rather than just deform
\citep{Tohline2001}. Both core and disk fragmentation are still
thought to be viable binary formation mechanisms. It is likely that
both mechanisms play a role in shaping the binary mass-ratio and
separation distributions. In the formation of higher-order multiples, it is even possible that both mechanisms operate in the same system.

@@

\subsection{Observing low mass-ratio binaries}
\label{paper1_sec:otherobs}
Detection of OB-star binaries with mass-ratio $q \approx 0.1$ or lower is very
difficult, since the ratio of the secondary flux $F_s$ to the primary
flux $F_p$ is $F_s/F_p \sim 10^{-3}$ or lower in the V-band. Imaging surveys
can detect such contrast ratios for wide orbits, but lose sensitivity
as the separation decreases below about $1^{\prime\prime}$
\citep[e.g.][]{Maiz2010}. Spectroscopic binary surveys do well for
short-period systems where a full orbit can be mapped in a reasonable
amount of time, but lose sensitivity for periods greater than about one year
\citep[e.g.][]{Sana2009, Evans2010}. However, low-mass companions ($q \lesssim
0.2$), which induce a small reflex motion on the primary, are very difficult to find with
traditional spectroscopic surveys.

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig1.pdf}
  \caption{This figure illustrates the approximate flux ratio limit to
  the detection method outlined in section
  \ref{paper1_sec:newmethod}. \emph{Top panel}: Residuals after telluric
  correction (see section \ref{paper1_sec:reduction}) for chip 2 of HIP 80582 are in black, with an
  atmosphere model for an $0.9 M_{\odot}$ star at 50.1 Myr below it in
  red. The flux ratio at this age is $F_s/F_p = 0.0092$. \emph{Middle panel}: The scaled model
  spectrum was added to the telluric residuals, and then the sum was
  cross-correlated with the model. Despite the signal being
  significantly below the noise level, the star was detected at a high
significance. The y axis, in units of the standard deviation of the
cross-correlation function, shows that the significance of the peak is over
$4\sigma$. \emph{Bottom panel}: Same as the middle panel, but the
model spectrum was added to the residuals with a 50 km s$^{-1}$ velocity
offset.}
  \label{paper1_fig:method}
\end{figure*}

In this paper, we introduce a technique that is sensitive to young binary
systems with secondary temperatures $4000$ K $\lesssim T_\mathrm{eff} \lesssim
6000 $K. For early B-type primaries with ages $\sim 15$ Myr, these
temperatures correspond to mass-ratios $q \approx 0.05-0.3$, right
where we expect to see binaries formed by disk instability (see
section \ref{paper1_sec:formation}). Rather
than attempting to detect the reflex motion of the parent
star as in exoplanet searches and SB1 binaries, we attempt to directly
detect the spectrum of the young low-mass companion using high
signal-to-noise, high-resolution data. There is a multitude of archived B-star observations in the near-infrared,
where they are used as telluric standard stars to remove the absorption spectrum of the Earth's atmosphere (telluric
lines). This method is equally sensitive to all separations within the point spread function, which is dominated by the seeing since the adaptive optics are not used in telluric standard star observations. A typical seeing of $\sim 0.8''$ corresponds to up to $\sim 900$ AU for targets within a few kpc. In this paper, we describe a search for young F5-K9 type companions in archived VLT/CRIRES spectra of 34 early B-type stars.

In section \ref{paper1_sec:newmethod} we describe our detection method in 
more detail. Section \ref{paper1_sec:sample} describes the B-star sample we use in this work.
Section \ref{paper1_sec:reduction} contains the data reduction and telluric correction methods. 
We summarize our results in section \ref{paper1_sec:results}. We examine the
completeness of our sample in section \ref{paper1_sec:completeness} and put
limits on the multiplicity fraction as a function of mass-ratio in
section \ref{paper1_sec:multiplicity}. Finally, we present our conclusions about the prevalence of low mass-ratio companions to early B-type stars and discuss how our results constrain star formation mechanisms in Section \ref{paper1_sec:conclusions}.

\section{Direct Spectral Detection Method}
\label{paper1_sec:newmethod}

We describe here our method to detect the emission from an
approximately solar-mass star orbiting an early B-type star, which we
will hereafter call the direct spectral detection method. The basis of
this method is to cross-correlate a high signal-to-noise ratio B-star
spectrum with a synthetic F,G, or K star spectrum. If a low-mass star
with such a spectrum is orbiting the B-star, we expect to find a peak
in the cross-correlation function at the radial velocity corresponding to
the low-mass star's motion. A peak in the cross-correlation
function should appear even if the
flux from the low-mass star is comparable to or even slightly less than the noise level in the
spectrum. Figure \ref{paper1_fig:method} illustrates the approximately limiting
case for the flux ratio. The top panel shows a fully reduced CRIRES spectrum of HIP 108975 (see section \ref{paper1_sec:reduction}) with a model spectrum for an $0.9 M_{\odot}$ star at a realistic flux ratio below it. We used
evolutionary tracks published by \cite{Landin2008} to evolve the secondary star
to 50.1 Myr, the age of the system \citep{Tetzlaff2010}, in order to determine the flux
ratio between the primary and secondary. The secondary star model was then added to
the telluric-corrected B-star spectrum at two different velocities. It is clear that the model spectrum has an amplitude much smaller
than the noise.  Nonetheless, the bottom two panels show that a cross-correlation will
have a peak with high significance at the velocity of the secondary star.

\begin{figure*}[t]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig2.pdf}
  \caption{\emph{Top panel}: The telluric spectrum (absorption due to Earth's
    atmosphere) in the wavelength range from $2290-2400$ nm. Most of the lines are
    from CH$_4$, with a few H$_2$O lines appearing in the right
    half. \emph{Bottom panel}: The model spectrum of a 5500 K star
    with $\log (g) = 4.0$ and solar metallicity. Note that the line density of telluric
    lines is comparable to or greater than that of the star model, and many of the
    telluric lines are stronger than the stellar lines.}
  \label{paper1_fig:telluric}
\end{figure*}

@@

There are two main difficulties with the direct spectral detection method: 
telluric line removal and the low flux ratio between the primary and secondary
star. Figure \ref{paper1_fig:telluric} shows the transmittance through the
Earth's atmosphere (the telluric spectrum) in the wavelength range we
are interested in. Most of the spectral lines are from methane, with a
few deep water lines towards the red end
of the range shown (See section \ref{paper1_sec:reduction} for details on the
telluric line removal). The low flux ratio makes the telluric
contamination especially troublesome, since the telluric lines are
stronger than the lines in the companion star spectrum. The flux ratio of $F_s/F_p
\sim10^{-2}$ effectively sets a lower limit on the signal-to-noise
ratio for which the direct spectral detection method is possible. 
Any flux coming from a low-mass star will be completely buried
in the Poisson noise for spectra with SNR $\ll100$. Removal of the 
telluric contamination will add more noise to the spectrum, so a spectrum
should have SNR of a few hundred \emph{before telluric line removal}
to have a good chance of detecting a companion.

\section{Star Sample}
\label{paper1_sec:sample}
B-type stars are commonly used in the near-IR as telluric
standard stars. Astronomers will observe their science targets, and
then move to a B-type star. Since B-type stars have few
spectral lines relative to cooler stars, most of the observed
spectral lines will be from the absorption of Earth's atmosphere
(telluric absorption). Therefore, these stars provide an empirical
estimate of the telluric spectrum; division of the science spectrum by
the normalized standard star spectrum will mostly remove the telluric
lines.

@@

To generate the sample, we started with all single, main sequence B0-B5 stars 
with CRIRES observations from 2300-2400 nm. We then excluded any shell stars, which have circumstellar disks \citep{Porter2003} that may create
false positives. Table \ref{paper1_tab:sample} shows the complete sample used in this
project. The spectral types and ages were obtained from a catalog of nearby
young stars \citep{Tetzlaff2010}. The one exception is HIP 97611, which was
not in \cite{Tetzlaff2010}. For this star, the age was taken from
\cite{Westin1985} and the spectral type from the Simbad database\footnote{\url{http://simbad.u-strasbg.fr/simbad/}}
. The distances to all stars were
determined from parallaxes given in the Simbad database. The maximum
separation column estimates the approximate maximum separation of the binary
orbit we are sensitive to, assuming a seeing of 0.8'' which is typical of
Paranal Observatory. The median of the maximum separations to which we are sensitive is 124
AU.  The final column gives the number of distinct observations of the
star. We count all nodding positions taken on a given night with the same 
detector wavelength setting as one observation.

@@

\section{Data Reduction and Telluric Correction}
\label{paper1_sec:reduction}
The data reduction was done using standard methods in
IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatories,
    which are operated by the Association of Universities for Research
    in Astronomy, Inc., under cooperative agreement with the National
    Science Foundation.}. All observations were taken in an AB or ABBA nodding
pattern. For each set of AB nods, A-B and B-A frames were made to
remove any atmospheric emission lines and dark current. The resulting
difference images were then treated to a quadratic nonlinearity correction, using
coefficients made available by the CRIRES
team%\footnote{\url{http://www.eso.org/observing/dfo/quality/CRIRES/pipeline/pipe_calib.html}}. 
The corrected frames were then divided by a normalized flat-field. Due
to the slit curvature, the spectrum can shift by up to a pixel in
the dispersion direction between the A and B nod positions. Therefore,
combining the 2D frames before extraction can reduce the spectral
resolution and affect the line shapes. For this reason, we
combined the nodding positions only after the wavelength
calibration and telluric correction. Each nod position was extracted using the 
optimal algorithm in the apall task in IRAF. The spectra were wavelength 
calibrated using a model telluric
spectrum generated with the atmospheric modeling code
LBLRTM%\footnote{\url{http://www.rtweb.aer.com/lblrtm_description.html}}
\citep{Clough2005}.

@@

The LBLRTM atmospheric modeling code comes with a molecular line list
based on the HITRAN 2008 database \citep{Rothman2009}, with a few
molecules individually updated. Since none of these updates were
relevant for the wavelength range from $2300 - 2400$ nm, we in
essence used the stock HITRAN 2008 database. However,
in the process of modeling, we found several water and methane lines
that were consistently under- or over-fit. For these cases, we
manually adjusted the line strengths in the database. The line
strengths were fit visually and should not be considered rigourous new line strengths. Table \ref{paper1_tab:linelist}
summarizes these changes.

@@

In order to minimize these spikes, we performed a second fit to any
residuals significantly above the continuum noise level. To make sure
we were not fitting away any low-mass star lines, we only corrected
spikes whose amplitude was greater than $5\%$ of the continuum level. In this
second fit, we first attempted to fit a Gaussian to each spike. If the
spike was well fit by a Gaussian, we divided the residuals by the fit.
If not, we
simply masked out the line core, so that it would not affect the
cross-correlation in later analysis (see section \ref{paper1_sec:newmethod}). Figure
\ref{correctionsteps} shows the steps involved in the telluric
correction. Notice that the secondary correction removes the
large residuals, while leaving the rest of the spectrum
unaffected.

@@

\section{Results}
\label{paper1_sec:results}
Each telluric residual spectrum was cross-correlated against a suite of model atmospheres
generated by the Phoenix stellar atmosphere code \citep{Hauschildt1999}. All model spectra had solar metallicity. The effective
temperatures ranged from $3000-7200$ K, in 100K intervals. We used
several surface gravities based on the stellar temperature. For the
model secondary stars with $3000 < T_\mathrm{eff} < 3600$, which would
have to be very young (and large) to be detectable, we used a $\log (g) = 3.5$. For the secondaries with
$3600 < T_\mathrm{eff} < 6500$, we used $\log (g) = 4.0$. Finally, we used
$\log (g) = 4.5$ for $T_\mathrm{eff} > 6500$, which can be detected
closer to the Main Sequence. We found that the surface gravity has only a very small
effect on the cross-correlation, which is more sensitive to the line
position than its precise width or depth. We
compiled a list of all cross-correlations that show a single peak with
at least $3\sigma$ significance. For a given telluric-corrected residual
spectrum, several model atmospheres may generate a significant peak at
the same velocity. This is because the model spectra of two stars
differing by only a few hundred kelvin are not very different. To keep from
counting peaks twice, we only counted the cross-correlation that
resulted in the most significant peak at a given velocity. We then attempted to
reject spurious peaks caused by the noise or incomplete telluric line
removal in a multi-stage process.

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper1_fig4.pdf}
  \caption{Cross-correlation for HIP 26713, using a 5600 K star model spectrum as template. The y-axis is in units of
    the standard deviation of the cross-correlation function. The peak is very near the maximum velocity of $|v_\mathrm{max}| = 256$ km s$^{-1}$, assuming a circular orbit (see equation \ref{paper1_eqn:vmax}). The likelihood of observing the system nearly edge on and at a quadrature point, so that $|v| \sim |v_\mathrm{max}|$, is $p \approx 0.01$. However, it is possible that the system has an eccentric orbit, effectively increasing $|v_\mathrm{max}|$.}
  \label{paper1_fig:hip26713}
\end{figure*}

Next, we determined whether the signal-to-noise ratio and telluric line removal in a given observation would allow us to detect the candidate companion star.
To do this, we added a model atmosphere with the
same temperature as the candidate to the telluric-corrected spectrum at 17 different radial
velocities ranging from -400 to 400 km s$^{-1}$. We do not expect to see any
peaks from real companions with $|v| > 400$ km s$^{-1}$, the approximate
radial velocity of a $1 M_{\odot}$ star orbiting a $10 M_{\odot}$ star
such that the stellar surfaces are in contact. The flux ratio of the model atmosphere to the primary was obtained by
interpolating pre-main-sequence evolutionary tracks from
\cite{Landin2008} at the age of the system, as well at age$\pm
\sigma_{age}$. The primary star ages for our sample are given in Table
\ref{paper1_tab:sample}. We cross-correlated each of these semi-synthetic
spectra against the model spectrum; if the largest
peak was at the correct velocity, we counted the star as
detected. If the star was not detected in the sensitivity
analysis at least $50\%$ of the time, we rejected the candidate.
The significance of the correct peak in the cross-correlation 
function can vary greatly, depending on where the stellar spectrum falls in 
relation to the telluric line residuals. Therefore, we cannot usually reject a peak
based solely on its significance.

@@

\begin{equation}
v_\mathrm{max} = \sqrt{\frac{2G(M_\mathrm{prim} + M_\mathrm{sec})}{R_\mathrm{prim}}} \cdot \frac{T_\mathrm{sec}}{T_\mathrm{prim}}
\label{paper1_eqn:vmax}
\end{equation}

where $M_\mathrm{prim}$ and $M_\mathrm{sec}$ are the masses of the primary and
secondary stars, respectively, and $R_\mathrm{prim}$ is the radius of the
primary star. The primary masses are given in \cite{Tetzlaff2010}, while
the radii and primary star temperatures were estimated from spectral type relations given in
\cite{CarrollOstlie}. An eccentric orbit could have a larger maximum velocity than
that estimated by equation \ref{paper1_eqn:vmax}, if the orbit was oriented
such that the the secondary star was moving directly towards or away from earth at or near
periastron. A star in an eccentric orbit cannot get so close to the
primary that they touch, and its \emph{average} distance must still be
far enough to allow for the observed secondary star temperature. These
conditions lead to a maximum eccentricity, given by

\begin{equation}
e_\mathrm{max} = 1 - \frac{v_\mathrm{max}^2 (R_\mathrm{prim} + R_\mathrm{sec})}{G(M_\mathrm{prim} + M_\mathrm{sec})}
\label{paper1_eqn:emax}
\end{equation}

where $R_\mathrm{prim} $ and $R_\mathrm{sec}$ are the radii of the primary
and secondary stars, respectively, and $v_\mathrm{max}$ is the maximum
circular velocity given by equation \ref{paper1_eqn:vmax}. Typical values
give $e_\mathrm{max} \approx 0.6$. Eccentricities near this value could
allow for velocities significantly greater than $v_\mathrm{max}$ given by
equation \ref{paper1_eqn:vmax}.

The above analysis is summarized in Table \ref{paper1_tab:rejection}. There
are two binary candidate systems that we have not been able to reject.
 For both of these, we checked what other observations the candidate
star had within the CO bandhead spectral region ($2300-2400$ nm). The analysis of each
of these stars is done separately below.

@@

\subsection{HIP 26713}
The cross-correlation for this candidate is shown in figure
\ref{paper1_fig:hip26713}. The strong peak at -220 km s$^{-1}$ has a
significance just over $4\sigma$, and corresponds to a 5600 K star
model. A sensitivity analysis (Table \ref{paper1_tab:rejection}, step 2) gives a median peak significance of $\sim 6\sigma$
with a large ($\sim 2\sigma$) spread. Due to the large spread, we cannot reject
the peak based on the observed significance.

The candidate radial velocity amplitude of 220 km s$^{-1}$ is very near the upper limit 
given by equation \ref{paper1_eqn:vmax} of 256 km s$^{-1}$. If this candidate is a real binary companion, it
must have been observed very near its radial velocity maximum and the orbital inclination must be very
near edge-on. Assuming a circular orbit and equal probabilities
of observing any given phase or inclination, the probability of this
occuring for this system is $\sim 0.01$. However, the probability for one system in our entire sample to be caught with this chance alignment rises to $0.14$.  In addition, we cannot discount the
possibility of an eccentric orbit leading to a higher value of $v_\mathrm{max}$ than estimated by equation \ref{paper1_eqn:vmax}. Without more data, we can neither confirm nor disprove the existence of a companion star orbiting HIP 26713.
